%-----------EDUCATION-----------%
\definecolor{myColor}{RGB}{18, 0, 40}
\definecolor{detalesColor}{RGB}{18, 0, 40}
\section{Projects}
\resumeSubHeadingListStart

% -------- Project 1 --------
\resumeSubheading
    {Dynamic QR Code Platform (QR Generator)}{\textcolor{titleColor}{{Full-Stack Web App}}}
    {\textcolor{titleColor}{\textbf{Laravel, Filament, Tailwind CSS}}}{\textcolor{titleColor}{\textbf{URL:} \href{https://qr.sawaedalriyadh.com/}{qr.sawaedalriyadh.com/}}}
\resumeItemListStart
    \textnormal{\textcolor{myColor}{\resumeItem{Developed a scalable QR code generation platform featuring dynamic content management, subscription-based monetization, and advanced analytics.}}}
    \textnormal{\textcolor{myColor}{\resumeItem{Implemented user authentication, role-based access, and an admin dashboard with Filament for seamless content management.}}}
    \textnormal{\textcolor{myColor}{\resumeItem{Built responsive UIs with social media links and real-time scan tracking with device and geographic insights.}}}
    \textnormal{\textcolor{myColor}{\resumeItem{Tech Stack: Laravel 12, PHP 8.4, MySQL, Livewire 3, Tailwind CSS 4, Filament 4, Pest, Docker (Laravel Sail), Git}}}
\resumeItemListEnd
\vspace{0.8\baselineskip}

% -------- Project 2 --------
\resumeSubheading
    {Event Management System with QR Code Attendance}{\textcolor{titleColor}{{Full-Stack Web App}}}
    {\textcolor{titleColor}{\textbf{Laravel, Livewire, Tailwind CSS}}}{\textcolor{titleColor}{\textbf{URL:} \href{http://events.arabdatahub.org}{events.arabdatahub.org}}}
\resumeItemListStart
    \textnormal{\textcolor{myColor}{\resumeItem{Architected and developed a scalable event management platform featuring QR code attendance tracking.}}}
    \textnormal{\textcolor{myColor}{\resumeItem{Role-based authentication, and automated email notifications with embedded QR codes.}}}
    \textnormal{\textcolor{myColor}{\resumeItem{Designed a responsive Arabic RTL interface and implemented dynamic interactions using Livewire components and custom Laravel middleware.}}}
    \textnormal{\textcolor{myColor}{\resumeItem{Tech Stack: PHP 8.4, Laravel 12, Livewire 3, MySQL, Tailwind CSS 4, Alpine.js, Docker (Laravel Sail), Git}}}
\resumeItemListEnd
\vspace{0.8\baselineskip}

% -------- Project 3 --------
\resumeSubheading
    {\textbf{Full Profile Website for Sawaed Al Riyadh}}{}
    {\textcolor{titleColor}{\textbf{Laravel, API, jQuery, Bootstrap}}}{\textcolor{titleColor}{\textbf{URL:} \href{https://sawaedalriyadh.com}{sawaedalriyadh.com}}}
\resumeItemListStart
    \textnormal{\textcolor{detalesColor}{
        \resumeItem{Designed and built the official website \href{https://sawaedalriyadh.com}{sawaedalriyadh.com}, delivering a responsive, user-friendly platform that highlights the company’s services and experience.}
    }}
\resumeItemListEnd
\vspace{0.8\baselineskip}

% -------- Project 4 --------
\resumeSubheading
    {\textbf{Full Profile Website for Mahasin Al-Sharq}}{}
    {\textcolor{titleColor}{\textbf{Laravel, API, Tailwindcss}}}{\textcolor{titleColor}{\textbf{URL:} \href{https://mahasinalsharq.com}{mahasinalsharq.com}}}
\resumeItemListStart
    \textnormal{\textcolor{detalesColor}{
        \resumeItem{Created a professional, responsive website for Mahasin Al-Sharq, improving the company’s online presence and service presentation.}
    }}
\resumeItemListEnd
\vspace{0.8\baselineskip}

% -------- Project 5 --------
\resumeSubheading
    {\textbf{Help Desk and Ticketing Software}}{}
    {\textcolor{titleColor}{\textbf{Laravel, Vue.js, API, jQuery, Bootstrap}}}{}
\resumeItemListStart
    \textnormal{\textcolor{detalesColor}{
        \resumeItem{Integrated full Arabic language support, developed a real-time warehouse stock management module, implemented a branch user ordering system, and optimized system performance for efficiency and reliability.}
    }}
\resumeItemListEnd

\resumeSubHeadingListEnd
